Technique for \earlywarning\ filtering for compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-29 introduction.tex
In section 1.1, removed some fluff in sentence about formation channels for proto-magnetars
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1186 ccdd05d5-56c1-461a-bf98-85f6876523b4
Cleared up a nonsensical statement about short GRBs in section 1.1 (if the light curve fades too quickly to catch the afterglow, then how do we know about short GRBs in the first place?
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1187 ccdd05d5-56c1-461a-bf98-85f6876523b4

Compact binary coalescence (\CBC) is thought to be a
mechanism for short gamma-ray bursts (short \GRB{}s) \citep{Lee:2005, nakar07}.
In this scenario, prompt gamma-ray emission arises on the accretion timescale
of a central compact object formed after the merger, $0.1$--$1.0$\,s
\citep{Janka1999}.  Interestingly, roughly a quarter to half of observed short
\GRB{}s also exhibit extended emission of $30$--$100$\,s in duration beginning
$\sim$$10$\,s after the \GRB{} and carrying comparable fluence to the initial
outburst.  Potential explanations for the emission are delayed fall-back
accretion caused by $r$-process heating \citep{Metzger2010} or the formation of
a proto-magnetar that interacts with
ejecta \citep{Bucciantini2011}.  In the case of the proto-magnetar, it might be
formed from accretion-induced collapse, or the merger of two \textsc{ns}s.  An
accompanying \GW{} observation would confirm the latter.

Optical flashes have only been observed for a handful of long \GRB{}s
\citep{2011CRPhy..12..255A} by telescopes with extremely rapid response or, in
the case of \textsc{grb 080319b}, by pure serendipity, where several telescopes
were already observing the afterglow of another \GRB{} in the same field of
view \citep{2008Natur.455..183R}. The observed optical flashes peaked within
tens of seconds and decayed quickly.  Short \GRB{}s, on the other hand,
typically fade too quickly to even catch the tails of the afterglows in any
band. Rapid \GW{} transient alerts could enable the first observation of prompt
optical flashes and the rise of afterglows from short \GRB{}s.

>>>>

Compact binary coalescence (\CBC) is thought to be a
mechanism for short gamma-ray bursts (short \GRB{}s) \citep{Lee:2005, nakar07}.
In this scenario, prompt gamma-ray emission arises on the accretion timescale
of a central compact object formed after the merger, $0.1$--$1.0$\,s
\citep{Janka1999}.  Interestingly, roughly a quarter to half of observed short
\GRB{}s also exhibit extended emission of $30$--$100$\,s in duration beginning
$\sim$$10$\,s after the \GRB{} and carrying comparable fluence to the initial
outburst.  Potential explanations for the emission are delayed fall-back
accretion caused by $r$-process heating \citep{Metzger2010} or the formation of
a proto-magnetar that interacts with
ejecta \citep{Bucciantini2011}.  A proto-magnetar may
form from accretion-induced collapse or the merger of two \textsc{ns}s.  An
accompanying \GW{} observation would confirm the latter.

Optical flashes have only been observed for a handful of long \GRB{}s
\citep{2011CRPhy..12..255A} by telescopes with extremely rapid response or, in
the case of \textsc{grb 080319b}, by pure serendipity, where several telescopes
were already observing the afterglow of another \GRB{} in the same field of
view \citep{2008Natur.455..183R}. The observed optical flashes peaked within
tens of seconds and decayed quickly.  Short \GRB{}s, on the other hand,
typically fade so quickly that it is difficult to catch even the tails of the afterglows in any
band. Rapid \GW{} transient alerts could enable the first observation of prompt
optical flashes and the rise of afterglows from short \GRB{}s.
